A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-18 tex/codatadp.tex
updated data

\begin{report}
\def\thewordpaper{report}
\newcommand\dotReportFootnote[1]{.\footnote{#1}}
\end{report}

@@

\begin{table*}[tbh!]
\normalsize
\begin{center}\begin{tabular}{l@{\kern1.5em}c@{\kern.5em}c@{\kern.5em}c@{\kern1.5em}c}
  & \HD{Distro} & \HD{AFP} & \HD{\gandl} & All
\\[1pt] %%% TYPESETTING HACK
\midrule
%$\enatT$
\\[-9pt] %%% TYPESETTING HACK
No (co)datatypes
  & 221 & 760 & \phantom{0}36 & 1017 \\
Datatypes without cyclicity
  & 227 & 765 & \phantom{0}36 & 1028 \\
Datatypes with cyclicity
  & 227 & 771 & \phantom{0}36 & 1034 \\
Codatatypes without bisimilarity
  & 217 & 787 & \phantom{0}34 & 1038 \\
Codatatypes with bisimilarity
  & 218 & 787 & \phantom{0}36 & 1041 \\
Full (co)datatypes
  & 224 & 798 & \phantom{0}36 & 1058 \\[\jot]
Total number of goals
  & 879 & 2974\phantom{0} & 117 & 3970
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}

>>>>

\begin{report}
\def\thewordpaper{report}
\renewcommand\dotReportFootnote[1]{.\footnote{#1}}
\end{report}

@@

\begin{table*}[tbh!]
\normalsize
\begin{center}\begin{tabular}{l@{\kern1.5em}c@{\kern.5em}c@{\kern.5em}c@{\kern1.5em}c}
  & \HD{Distro} & \HD{AFP} & \HD{\gandl} & All
\\[1pt] %%% TYPESETTING HACK
\midrule
%$\enatT$
\\[-9pt] %%% TYPESETTING HACK
No (co)datatypes
  & 221 & 760 & \phantom{0}57 & 1038 \\
Datatypes without cyclicity
  & 227 & 765 & \phantom{0}57 & 1049 \\
Datatypes with cyclicity
  & 227 & 771 & \phantom{0}57 & 1055 \\
Codatatypes without bisimilarity
  & 217 & 787 & \phantom{0}55 & 1059 \\
Codatatypes with bisimilarity
  & 218 & 787 & \phantom{0}58 & 1063 \\
Full (co)datatypes
  & 224 & 798 & \phantom{0}58 & 1080 \\[\jot]
Total number of goals
  & 879 & 2974\phantom{0} & 317 & 4170
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}
